Tables

### 2018-11-02 code/codebook_collated_summary_data.rmd
Updated project name in header in code files

---
dataMaid: yes
title: Codebook for collated_summary_data.csv
subtitle: "Limited evidence for widespread heterogeneity in psychology"
output: pdf_document
documentclass: article
header-includes:
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
  - \renewcommand\familydefault{\sfdefault}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data report overview
The dataset examined has the following dimensions:

>>>>

---
dataMaid: yes
title: Codebook for collated_summary_data.csv
subtitle: "Heterogeneity in direct replications in psychology and its association with effect size"
output: pdf_document
documentclass: article
header-includes:
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
  - \renewcommand\familydefault{\sfdefault}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data report overview
The dataset examined has the following dimensions:

### 2018-11-02 code/tables.rmd
Corrected footnote of Table 3
Updated project name in header in code files

---
title: "Tables"
author: "Limited evidence for widespread heterogeneity in psychology"
output: pdf_document
---

@@

het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Effect size estimate", "$I^2$(\\%)", "$I^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 7, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 7, "Statistical power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, k = no. primary studies, Estimate = Point estimates of effect sizes, $I^2$ 95\\\\% CI = $I^2$ 95\\\\% confidence interval. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/",
           alphabet = "These effects were simulated as standardized mean differences")

>>>>

---
title: "Tables"
author: "Heterogeneity in direct replications in psychology and its association with effect size"
output: pdf_document
---

@@

het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Effect size estimate", "$I^2$(\\%)", "$I^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 7, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 7, "Statistical power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, k = no. primary studies, Estimate = Point estimates of effect sizes, $I^2$ 95\\\\% CI = $I^2$ 95\\\\% confidence interval. Statistical power was simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/",
           alphabet = "These effects were simulated as standardized mean differences")
